Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
Masses

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). The posterior distribution for
$N_{\rm lens}$ also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures.\label{fig:masses2}}
\end{center}
\end{figure}

@@

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower. Related to this, we can
compute posterior probabilities for any hypothesis about the substructure
masses. With 95\% probability the substructure mass is less than 88 units
and with 75\% probability it is less than 54 units.

>>>>

The joint posterior distribution for the SIE mass total substructure mass
for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
the simulated data (Figure~\ref{fig:masses}), we see an expected negative
correlation between these two quantities. However, the points are not as
smoothly distributed in this case (we discuss this issue further
in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
95\% posterior probability, is $5.21 \pm 0.02\times 10^{12} M_\odot$
The posterior distribution for
$N_{\rm lens}$ (Figure~\ref{fig:N_lens2})
also shows some evidence for more than zero substructures.
In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
This corresponds to a Bayes Factor of approximately 3 in favour of
$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. Assuming a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc, one mass unit corresponds to 2.07$\times 10^{11} M_\odot$.
\label{fig:masses2}}
\end{center}
\end{figure}

@@

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower. Related to this, we can
compute posterior probabilities for any hypothesis about the substructure
masses. With 95\% probability the substructure mass is less than 88 units
and with 75\% probability it is less than 54 units. Clearly, it is not the
substructure mass over the entire domain that is of interest.
